\section*{Projects}

\project
  {Tiara}
  {https://git.new/tiaraweb}
  {Next.js, TypeScript, Next-Auth, Three.js, Framer Motion, Prisma, PostgreSQL}
  {
    \item Implemented \textbf{OAuth-based authentication} using \textbf{Next-Auth}, enabling secure user registration and session management across the platform.
    \item Migrated from a static role system to a \textbf{database-driven RBAC model} with \textbf{Prisma} and \textbf{PostgreSQL}, and optimized the \textbf{email queue} to handle burst traffic without message loss.
  }

\project
  {Codelyra}
  {https://git.new/codelyra}
  {TypeScript, Discord.js, Docker}
  {
    \item Engineered a \textbf{Discord bot} capable of compiling and executing code across \textbf{600+ programming languages} via a containerized \textbf{Docker} sandbox.
    \item Designed \textbf{interactive slash commands} with real-time feedback, increasing \textbf{user engagement by 20\%} over the first month of deployment.
  }

\project
  {Certificate Generator}
  {https://git.new/gdsccert}
  {Python, NumPy, Pillow}
  {
    \item Automated \textbf{bulk certificate generation} by dynamically compositing recipient data onto design templates using \textbf{Pillow}, processing hundreds of records in seconds.
    \item Exported certificates as \textbf{print-ready PDFs} with configurable \textbf{fonts, themes, and layouts} via a CLI interface.
  }

\project
  {Sorting Algorithm Visualizer}
  {https://git.new/sortalgviz}
  {C++, OpenGL, CMake}
  {
    \item Rendered \textbf{real-time step-by-step visualizations} of \textbf{Bubble, Merge, Quick, and Insertion Sort} using \textbf{OpenGL}, with adjustable speed controls.
    \item Demonstrated \textbf{parallel sort execution} side-by-side, providing direct visual comparison of algorithmic performance.
  }

\project
  {TL;DR News}
  {https://git.new/tldrnews}
  {Flutter, TypeScript, Dart}
  {
    \item Built a \textbf{cross-platform news app} in \textbf{Flutter} that scrapes and surfaces summarized articles from \textbf{tldr.tech}, targeting developers who prefer concise updates.
    \item Handled \textbf{asynchronous API requests} in \textbf{TypeScript} with error boundaries and caching, ensuring smooth performance on low-bandwidth connections.
  }
